---
title: "Case2 - Spatial statistics"
output: html_document
date: "2024-04-30"
---

## Chapter 11 - Image Data - Case 2 Spatial statistics

A case study: Interaction between immune cells and cancer cells
Data source: https://web.stanford.edu/class/bios221/data/

This work excludes
11.15.2 Convex hull
11.15.3 Other ways of defining the space for the point process
11.16 First order effects: the intensity
11.17 Second order effects: spatial dependence
And the exercises

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#BiocManager::install("genefilter")
#Libraries
library(EBImage)
library(htmlwidgets)
library(ggplot2)
library(cba)
library(genefilter)
library(GGally)
library(tibble)

library(readr)
library(dplyr)
library(spatstat)
```

### 1. Import and inspection
```{r}
cellclasses = c("T_cells", "Tumor", "DCs", "other_cells")
brcalymphnode = lapply(cellclasses, function(k) {
    read_csv(file.path("data", sprintf("99_4525D-%s.txt", k))) |>
    transmute(x = globalX, y = globalY, class = k)
}) |> bind_rows() |> mutate(class = factor(class))

brcalymphnode

```

```{r}
table(brcalymphnode$class)
```



```{r}
ggplot(filter(brcalymphnode, class %in% c("T_cells", "Tumor")),
   aes(x = x, y = y, col = class)) + geom_point(shape = ".") +
   facet_grid( . ~ class) + guides(col = "none")
```

convert our data in brcalymphnode into an object of class ppp; we do this by calling the eponymous function.
ppp objects are designed to capture realizations of a spatial point process, that is, a set of isolated points located in a mathematical space;
```{r}
ln = with(brcalymphnode, ppp(x = x, y = y, marks = class, 
                             xrange = range(x), yrange = range(y)))
ln
```



